\documentclass{article}
\linespread{1.5}
\usepackage[utf8]{inputenc}
\usepackage{color}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{textcomp}

\usepackage{enumerate}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[R]{Caner Derici}
\fancyfoot[C]{\thepage}

% \usepackage{lipsum}

\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
\newcommand{\Hrule}{\rule{\linewidth}{0.3mm}}

\makeatletter% since there's an at-sign (@) in the command name
\renewcommand{\@maketitle}{
  \parindent=0pt% don't indent paragraphs in the title block
  
  {\Large \bf \@title}
  
  \Hrule%
    
  \textit{\@author \hfill \@date}
  \par
}
\makeatother% resets the meaning of the at-sign (@)
\date{Caner Derici}
\title{Y790-32707 - Assignment 8: Editing for Conciseness}
\author{}


\begin{document}
%\pagenumbering{gobble}

\maketitle% prints the title block

\section*{Exercise 5.1}

\begin{enumerate}

\item Critics cannot avoid employing complex and abstract technical terms in order to successfully analyze literary texts and discuss them in a meaningful way.

\item Scientific research depends on accurate data to offer theories that will allow the world to advance into the future in a cautious way. 

\item In regard to prospects for employment in teaching positions, the future is uncertain for those who engaged in studies at the graduate school.

\item Various agencies that provide aid to those who participate in our program have recently announced to reverse themselves from returning to the original policy established earlier.

\item In spite that the educational environment is a very significant facet to every one of our children in terms of his or her future development, different groups do not support fair tax assessments that are required for providing a quality educational experience. 

\item A majority of all patients at a public medical facility do not expect special medical attention because their health problems are often of a minor nature and can be adequately treated with minimal understanding. 

\item Despite that all legal restrictions on the use of firearms are the subject of heated debate, the general public should continue discussions pro and con in regard to them.

\item Under circumstances in which individuals with financial resources anticipate the possibility that the goods and services may continue to increase in price, they will ordinarily put a majority of the discretionary financial resources into specific objects of artistic value.

\item When the governors of the various states have the opportunity to discuss matters of economic needs in their respective states, it is possible that they will find a way to overcome the major problem of specifying how to distribute Federal economic resources to their different states.

\item Those engaged in the profession of education have for a long time, had an interest in better understanding about the improvements in how individuals commit information from textual material to memory.  The first problem is identifying common and different features among passages. The second is assigning some kind of value to the quality and quantity of information that a reader does not forget after reading.

\end{enumerate}
  
\section*{Exercise 5.3}

% What single words can you find for the negative phrases in these sen-tences? Each was in an earlier draft of this book and revised.

\begin{enumerate}

\item While the standard definition of a verb as an action word is \textbf{unreliable}, it is in fact not \textbf{misadvice}.

\item A second set of rules includes those whose observance we \textbf{miss}, and whose violation we \textbf{miss} too.

\item But we ought \textbf{reject} the argument that we don't need the word finalize, or that it is ugly because of the -ize.

\item While it is \textbf{unclear} what counts as "too many" prepositions, it is clear that when you don't use abstract nouns, you don't need most of the prepositional phrases.

\item These choices among points of usage let those among us who wish to do so express our sense of linguistic decorum, a decorum that many of us believe testifies to our precision.
  It is an impulse we ought \textbf{approve}, so long as it is \textbf{competent} and thoughtful.

\end{enumerate}

%% \begin{thebibliography}{1}

%% \bibitem{www}
%% E. Başar, C. Derici, Ç. Şenol, \emph{WorldWithWeb: A compiler from world applications to JavaScript}, In proceedings of The Scheme and Functional Programming Workshop\hskip 1em plus 0.5em minus 0.4em\relax Boston, Massachusetts, 2009.

%% \end{thebibliography}


\end{document}
